```{r}
#multiple hobbies
hobby = c(
  'sport, reading, movie',
  'sport',
  'movie, sport, reading',
  'movie, Reading',
  'sport') 

```

```{r}
'sport, reading, movie'=='reading, sport, movie'
'sport, reading, movie'=='sport, reading, movie'#sequence
hobby=="reading"
hobby%in%"reading"
hobby%in%'sport, reading, movie'
```
```{r}
stringr::str_detect(
  'reading, sport, movie',
  'reading'
)
```

```{r}
# any one likes to read
stringr::str_detect(hobby, "reading") # 4th is FALSE
stringr::str_detect(hobby, 
                    coll("reading", ignore_case = T)) # 4th is TRUE
```
```{r}
stringr::str_split(
  string,
  pattern=","
)
```

```{r}
# Count for each hobby
table(hobby)

unlisted_hobbies <- {
  hobby |> 
    stringr::str_split(", ") -> list_hobbies
  
  unlist(list_hobbies)
}
table(unlisted_hobbies)
```
```{r}
love1<-{love2<-stringr::str_split(
  hobby,
  pattern=","
)
table(unlist(love2))
}
love2
love1

```
```{r}
toupper(hobby)|>table()
tolower(hobby)|>table()
```
```{r}
df_dates =
  data.frame(
    year = c('2001','2001','2002','2001','2001'),
    month = c('4','10','1','1','4'),
    day = c('3','3','22','18','3')
  )
```
```{r}
chr_dates <- paste(df_dates$year, df_dates$month, df_dates$day,sep="-")
chr_dates 
dates <- lubridate::ymd(chr_dates)
dates
```
```{r}
students <-
  data.frame(
    major = c('economics','sociology','economics','sociology','sociology','finance','sociology','statistics','statistics','sociology'),
    year= c(4,1,4,3,1,4,4,2,1,3),
    credits= c(16,13,10,21,17,12,21,15,20,17)
  )
```
school(學院)
```{r}
school = character(10)

{
  # For those whose major is economics or sociology, their school is social science. 
  pick_those = students$major %in% 
    c("economics", "sociology")
  school[pick_those] = "social science"
  
  # For those whose major is statistics or finance, their school is business
  pick_those = students$major %in% 
    c("statistics", "finance")
  school[pick_those] = "business"
}

school
```
```{r}
school = factor(students$major)

{
  levels(school) <- 
    c("social science","business","social science","business") #RHS and LHS are same length
  
  school
}

school
```
```{r}
students$year<-factor(students$year)
students$year
levels(students$year)<-c(
  "freshman","sophemore",
  "junior","senior"
)
students$year
```

```{r}
students$credits
```
credits: <= 12 (light), 13-20 (normal), 20+ (heavy)
```{r}
workload<-character(10)

workload[c(3,6)]<-"light"
workload[c(1,2,5,8,9)]<-"normal"
workload[c(4,7,10)]<-"heavy"
workload
```
```{r}
workload<-character(10)
pick_those= students$major <=12
workload[pick_those]="light"

pick_those2=(students$major>=13)|(students$major<=20)
workload[pick_those2]="normal"

pick_those3= students$major >20
workload[pick_those3]="heavy"
workload
```

```{r}
workload<-factor(students$credits)
levels(workload)
```
```{r}
## step 1. create cut points vector (each point is maximal value of a group)
maximalValues <- c(0, 12, 20, 30) # throw in a lowest value (0)
## step 2: cut students$credits with maximalValues cut points
cut(
  students$credits,#numerical vector
  maximalValues #cut points
  ) -> students$load
## step 3(optional): using regroup skill to rename levels
levels(students$load) <- c("light", "normal", "heavy")
students$load
```

```{r}

dates <- 
  c('2016-11-15','NA','NA','1997-05-07','1995-08-25','2002-09-20','NA','NA','NA','1995-07-16', '2011-06-22')
grades <- c(29,53,26,27,55,69,NA,NA,63,NA,56)
genders <- c('Male','Female','Male','Male','Female','Female',NA,'Male','Male','Female','Female')
majors <- c('economics','economics',NA,'economics','economics','economics','economics','statistics','law','economics','law')
)
```
 
```{r}
dates |> class()
dates |> lubridate::ymd() -> dates
dates |> class()
```
```{r}
analysis <- list()
anyNA(dates)
dates |> is.na() |> sum() -> analysis$dates$na$sum
anyNA(grades)
grades |> is.na() |> sum() -> analysis$grades$na$sum
```



```{r}
dates |> range()
dates |> range(na.rm=T) -> analysis$dates$range

grades |> range(na.rm=T) -> analysis$grades$range
grades |> median(na.rm=T) -> analysis$grades$mdian

grades |> mean(na.rm=T) -> analysis$grades$mean
```

