
```{r}
dayinfro<-list()
dayinfro$ymd<-c("30/10/2021", "30-10-2021", "30 October, 2021", "30 Oct., 2021")
class(dayinfro$ymd)
lubridate::as_date(dayinfro$ymd)->
  dayinfro$ymd_parsed
class(dayinfro$ymd_parsed)
```
```{r}
dateTime_taipei <- 
  lubridate::ymd_hms(
    c("2021/10/30 13:22:52", "2021-10-31 1:22:52PM"),
    tz = "Asia/Taipei")
dateTime_taipei
```
```{r}
dateTime_london <- 
  lubridate::mdy_hm(
    c("October 30, 2021, 23:10", "Oct. 30, 2021 `
```{r}
c(dateTime_taipei,dateTime_london)
```
```{r}
dateTime_london_atTaipei <-
  lubridate::with_tz(
    dateTime_london,#must be a date time class
    tz="Asia/Taipei"
  )
dateTime_london
dateTime_london_atTaipei
```

```{r}
datetime_boston<-
  lubridate::mdy_hm(
    c("10/13/2020 15:00", "4/10/2019 09:30"),
    tz="America/Bogota"
  )
datetime_mykonos<-
lubridate::mdy_hm(
  c("1/14/2021 03:27", "8/8/2020 11:20"),
  tz="Europe/Mariehamn")

dateTime_boston_atDeli <-
  lubridate::with_tz(
    datetime_boston,
    tz="Asia/Calcutta")
dateTime_mykonos_atDeli <-
  lubridate::with_tz(datetime_mykonos,tz="Asia/Calcutta")

```








```{r}
survey_df_1step <-
  data.frame(
    list(
    age=c(54, 32, 28, 20), # age
    gender=c("male", "female", "female", "male"), # gender
    residence=c("north", "south", "east", "east"), # residence
    income=c(100, 25, NA, 77) # income
 ) )
class(survey_df_1step)
```


```{r}
```


```{r}
survey_fbf2 <-
  list(
    age=list(54, 32, 28, 20), 
    gender=list("male", "female", "female", "male"), 
    residence=list("north", "south", "east", "east"), 
    income=list(100, 25, NA, 77))
````


```{r}
commonclass<-list()
commonclass$data_frame<-data_frame<-survey_df_1step
```

```{r}
data.frame(survey_df_1step)
```
```{r}
dfExercise <- list()

dataSet1 <- list(
  name=c("John", "Mary", "Ben"),
  age=c(33, 45, NA)
)
data.frame(dataSet1)
dataSet1<-dfExercise$data1.
```

```{r}
dataSet1$children[[1]][[1]] <-c(name="Jane",age=2)
dataSet1$children[[2]][[1]] <-c(name="Bill",age=3) 
dataSet1$children[[2]][[2]] <-c(name="Ken",age=0)
dataSet1$children[[3]][[1]] <-c(name="William",age=10)

```

