```{r}
c(2, 5, 7) + 3 # work
list(2, 5, 7) + 3 # won't work
```
```{r}
mylist <- list(2, 5, 7)
mylist[[1]] <- mylist[[1]]+3
mylist[[2]] <- mylist[[2]]+3
mylist[[3]] <- mylist[[3]]+3
print(mylist)
```

```{r}
examples <- list()
examples$unlist$source1 <-
  list("A", "B", "C")
examples$unlist$result1 <- 
  unlist(examples$unlist$source1)
print(examples$unlist$source1)
print(examples$unlist$result1)

class(examples$unlist$source1)
class(examples$unlist$result1)
```


```{r}
```examples$unlist$source2 <- 
  list(
    list("A", "B", list("C")),
    list("D"),
    "E"
  )
examples$unlist$result2 <- 
  unlist(
    examples$unlist$source2
  )

print(examples$unlist$source2)
print(examples$unlist$result2)
class(examples$unlist$source2)
class(examples$unlist$result2)
```

```{r}
examples$unlist$source3 <- list(5, 6, 7)
examples$unlist$result3 <-
  unlist(
    examples$unlist$source3
  )

class(examples$unlist$source3) # list class
```


```{r}
class(examples$unlist$result3) # numeric class
```



```{r}
namedList <- list(name="John", spouse="Mary")

unlist(
  namedList
) -> unlist_namedList

unlist_namedList
```

```{r}
lgl <- c(TRUE, FALSE)
num <- c(0.2, 3, 0)
as.character(lgl)#the same as c("TRUE","FALSE")
as.character(num)#the same as c("0.2","3")
```
```{r}
num + 3
```
```{r}
tookRcourse <- c(TRUE, FALSE, TRUE, TRUE)
as.numeric(tookRcourse)
howManyTookR <- sum(
  as.numeric(tookRcourse)
)
print(howManyTookR)
howManyTookR <- sum(tookRcourse)
print(howManyTookR)
```
```{r}
which(tookRcourse)#apply to only logical vector
```
```{r}
as.numeric(c("1","5"))+3

```
```{r}
ming_guoDates <- c("1100822","1090723") # 民國100-8-22，民國109-7-23

# 民國1年 is 1911
westernDates <- 
  as.numeric(ming_guoDates) +
  19110000

westernDates 

lubridate::ymd(westernDates)
```
```{r}
# on numeric vector
# tell us if the number is not zero
print(num)
as.logical(num)
```
```{r}
# only person with a non-zero wage has a job
wage <- c(3000, 2000, 0, 1000)
haveJob <- as.logical(wage)
haveJob
```
```{r}
whoHasAJob <- which(haveJob)
whoHasAJob

# the wages of those who have a job
wage[whoHasAJob]
```
'[ ]' can also use logical vector to pick your values
```{r}
wage <- c(3000,2000,0,1000)
#want to pick up 3000 and 1000
wage[c(1,4)]
wage[c(T,F,F,T)]
```

```{r}
fct <- factor(
  c('參','貮','貮','貮','壹','貮','參','貮','參','參'),
  levels=c('壹','貮','參')
  )

dt <- lubridate::ymd_hms(
  c('2012-08-25 19:36:00','2018-01-06 10:44:00','2010-03-08 00:56:00')
)
```

```{r}
print(fct)
as.character(fct)

typeof(fct)
as.numeric(fct) # the positions in levels
```
```{r}
print(dt)
as.character(dt)

typeof(dt)
as.numeric(dt) # how many seconds past 1970-01-01 00:00
dt
dt + 30 # add 30 seconds
dt + 60*60 # add 1 hour
```
```{r}
x0 <- 1595950405 # the number of seconds
lubridate::as_datetime(x0)
location_history <- jsonlite::fromJSON("https://www.dropbox.com/s/db2vt4w9u2w7onx/Location%20History.json?dl=1")
```
```{r}
print(location_history$locations$timestampMs)
location_history$locations$timestampMs/(10**3)
timeStampMs_as.numeric <- 
  as.numeric(
    location_history$locations$timestampMs
  )
timeStamp_inSecondUnit <-
  timeStampMs_as.numeric/(10**3)

timeStamp_dateTimeClass <-
  lubridate::as_datetime(
    timeStamp_inSecondUnit
  )
```
```{r}
timeStamp_dateTimeClass <- 
  {result1<-as.numeric(location_history$locations$timestampMs)
    # Step 1: convert character to numeric
    result1/1000->result2
    # Step 2: given step 1 result, change millisecond to second unit
    lubridate::as_datetime(result2)
    # Step 3: given step 2 result, convert numeric seconds to date/time class
    
  }

```




```{r}
timeStamp_dateTimeClass2 <- 
  {
    # Step 1: convert character to numeric
    as.numeric(location_history$locations$timestampMs) -> step1
    
    # Step 2: given step 1 result, change millisecond to second unit
    step1/(10**3) -> step2
    
    # Step 3: given step 2 result, convert numeric seconds to date/time class
    lubridate::as_datetime(step2)
  }
timeStamp_dateTimeClass2 
```

```

